---
title: "Lab 5"
author: "Erin de Leon Sanchez"
date: "10/25/2021"
output: 
  html_document: 
    theme: spacelab
    toc: yes
    code_folding: hide
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

### Part 1 

In this section, we'll use the `t.test()` function to calculate confidence intervals.

### Example 1

Create a single mock sample containing a number of values, then learn to use `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible too.

```{r}
# Create a mock sample
otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29)

# Find the confidence interval:
otter_ci <- t.test(otter_lengths)

# Find the standard deviation
otter_sd <- sd(otter_lengths)
```
Confidence interval: We would expect, if we took multiple samples from this pop and calculated a CI for each of them, we expect 95% of those CIs could contain the true population mean. 

Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n = 8) with a 95% confidence interval of [29.1, 44.7] inches. 

What's important to include? sample size (n), some measure of sample spread (ex: SD)

objectname$valuename 
ex: `otter_ci$conf.int`
gives us a tool to pull pieces of information (elements) as long as you created the object and stored it

### Now, using in-line referencing

Mean otter length is `r round(otter_ci$estimate, 1)` inches.


