---
title: "Lab 5"
author: "Erin de Leon Sanchez"
date: "10/25/2021"
output: 
  html_document: 
    theme: spacelab
    toc: yes
    code_folding: hide
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

### Part 1 

In this section, we'll use the `t.test()` function to calculate confidence intervals.

### Example 1

Create a single mock sample containing a number of values, then learn to use `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible too.

```{r}
# Create a mock sample
otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29, 90, 72, 112)

# Find the confidence interval:
otter_ci <- t.test(otter_lengths)

# Find the standard deviation
otter_sd <- sd(otter_lengths)
```
Confidence interval: We would expect, if we took multiple samples from this pop and calculated a CI for each of them, we expect 95% of those CIs could contain the true population mean. 

Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n = 8) with a 95% confidence interval of [29.1, 44.7] inches. 

What's important to include? sample size (n), some measure of sample spread (ex: SD)

objectname$valuename 
ex: `otter_ci$conf.int`
gives us a tool to pull pieces of information (elements) as long as you created the object and stored it
if you want to specify the value... `objectname$valuename[#]`

### Now, using in-line referencing
Writing in-line code is important for reproducible code! 

Mean otter length is `r round(otter_ci$estimate, 1)` inches with a 95% confidence interval of [`r round(otter_ci$conf.int[1])`, `r round(otter_ci$conf.int[2])`] inches.

## Part 2: Two-sample t-tests

### Example 1

Make two mock samples, and ask the question: do we have sufficient evidence to make us reject the null hypothesis that these samples were drawn from populations with the same mean?

```{r}
# Make my mock samples
oak_trees <- c(20, 19, 24, 28, 34, 12, 15, 25)
  
pine_trees <- c(39, 26, 20, 30, 37, 22, 19, 18)

# Two-sample t-test
trees_t <- t.test(oak_trees, pine_trees)

# Null hypothesis: mean heights are the same 
# i.e. Trees are drawn from populations with the same mean height
```

The mean heights of oak and pine trees were (X+- Y) and (X +- Y), respectively, and the difference was not significant (t(`r trees_t$parameter`) = `r round(trees_t$statistic, 1)`,  p = `r trees_t$p.value`).

#"two-sample t-test; t(df) = t-statistic, p = p-value"


## Part 3: Another t-test with cars data

Using the `mpg` dataset 

### Take a look at the data

```{r}
compact_suv <- mpg %>%  
  filter(class %in% c("compact", "suv"))

# Check for remaining levels
unique(compact_suv$class)
```

Create a histogram of city gas mileage (city) faceted by class starting from compact_suv. 
```{r}
ggplot(data = compact_suv, aes(sample = cty)) +
  geom_qq() +
  facet_wrap(~ class)
```
Find some summary statistics for each group. 

```{r}
car_stats <- compact_suv %>% 
  group_by(class) %>% 
  summarize(
    mean_city = mean(cty),
    sd_cty = sd(cty),
    sample_size = n()
  )

car_stats
```
The t.test() function REALLY wants vectors of things. Use the `pull()` function to pull out a vector from a data frame.

```{r}
compact_sample <- compact_suv %>% 
  filter(class == "compact") %>% 
  pull(cty)

# Your turn: do the same thing to get a vector of city gas mileages for SUVs

suv_sample <- compact_suv %>% 
  filter(class == "suv") %>% 
  pull(cty)
```


H0: Mean city gas mileages for SUVs and compact cars are the same

```{r}
t.test(compact_sample, suv_sample)
```

Conclusion: Reject the null hypothesis that the gas mileages are the same

There is a significant difference in mean city gas mileage for SUVs and compact cars (t(df), t-statistic, p < 0.001). 
